---
title             : "Consequences of a structural construal for normativity, possibility of change, intervention"
shorttitle        : "Title"

author: 
  - name          : "Marianna Y. Zhang"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Building 420, 450 Jane Stanford Way, Stanford, CA 94305"
    email         : "marianna.zhang@stanford.edu"
  - name          : "Ernst-August Doelle"
    affiliation   : "1"

author: 
  - name          : "Ellen M. Markman"
    affiliation   : "1"
    corresponding : no
    address       : "Building 420, 450 Jane Stanford Way, Stanford, CA 94305"
    email         : "markman@stanford.edu"
  - name          : "Ernst-August Doelle"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Stanford University"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "structural thinking, categories, explanation, normativity, possibility of change"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
require("knitr")
#library("papaja")  # not available for R 4.0
library(here)       # setting directory
library(tidyverse)  # tidying and wrangling data, visualizations
library(ggthemes)   # visualization themes for ggplot2
library(corrplot)   # correlation plots
library(lmerTest)   # linear mixed effects model
library(brms)       # Bayesian mixed effects model
library(tidybayes)  # Bayes factor

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r vis-theme}
# Set visualization theme
theme_set(
  ggthemes::theme_few() +
  theme(text = element_text(size = 16)) # large text size for presentation figures
)

condition_colors = c("internalist_biological" = "#49808C",
                     "Internalist (biological)" = "#49808C",
                     "internalist_cultural" = "#F2BF80",
                     "Internalist (cultural)" = "#F2BF80",
                     "structural" = "#D9695F",
                     "Structural" = "#D9695F")

intervention_colors = c("modify Zarpies biology" = "#49808C",
                        "modify Zarpies beliefs/culture" = "#F2BF80",
                        "acquire okinberries" = "#D9695F",
                        "modify okinberries" = "#D9BAB7",
                        "acquire pogoberries" = "#C3C7B6",
                        "other" = "#D9D9D9",
                        "ambiguous" = "#D9D9D9",
                        "don't know" = "#9E9E9E")
```


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) --> 

This project's [repository](https://github.com/mariannazhang/structural-consequences) and [preregistration](https://osf.io/hz76n/) can be found online.


```{r predictions-simulation}
## Fixme: turn into power analysis

# Simulation, given children's predicted responses
sample_size = 150
condition_size = sample_size/3

# Possibility of change & normativity
predicted <- tibble(
  # Set up table
  condition = rep(c("Internalist (biological)", "Internalist (cultural)", "Structural"), each = condition_size * 2), #*3 because 3 measures
  measure = rep(c("Possibility of change", "Normativity"), each = condition_size, times = 3), #*3 conditions
  participant = c(rep(seq(from = 1, to = condition_size, by = 1), times = 2),
                  rep(seq(from = condition_size + 1, to = condition_size*2, by = 1), times = 2),
                  rep(seq(from = condition_size*2 + 1, to = condition_size*3, by = 1), times = 2)),
  
  
  # Simulate responses
  response = 
    c(#Internalist (biological): Possibility of change
      sample(c(1, 2, 3, 4), # response options
             size = condition_size,
             replace = TRUE,
             prob = c(0.4, 0.4, 0.2, 0.1)), # weighted mean = 2.2 of 1-4
      #Internalist (biological): Normativity
      sample(c(1, 2, 3, 4, 5, 6), 
             size = condition_size, 
             replace = TRUE,
             prob = c(0.05, 0.1, 0.15, 0.2, 0.3, 0.2)), # weighted mean = 4.2 of 1-6
      
      
      #Internalist (cultural): Possibility of change
      sample(c(1, 2, 3, 4), 
             size = condition_size, 
             replace = TRUE,
             prob = c(0.2, 0.4, 0.25, 0.15)), # weighted mean = 
      #Internalist (cultural): Normativity
      sample(c(1, 2, 3, 4, 5, 6), 
             size = condition_size, 
             replace = TRUE,
             prob = c(0.05, 0.1, 0.15, 0.25, 0.3, 0.15)), # weighted mean = 4.1 of 1-6
      
      #Structural: Possibility of change
      sample(c(1, 2, 3, 4), 
             size = condition_size, 
             replace = TRUE,
             prob = c(0.1, 0.2, 0.4, 0.3)), # weighted mean = 2.9 of 1-4
      #Structural: Normativity
      sample(c(1, 2, 3, 4, 5, 6), 
             size = condition_size, 
             replace = TRUE,
             prob = c(0.1, 0.3, 0.25, 0.2, 0.1, 0.05)))
)

# Target of intervention
predicted_intervention <- tibble(
  # Set up table
  condition = rep(c("Internalist (biological)", "Internalist (cultural)", "Structural"), each = condition_size * 1), #*3 because 3 measures
  measure = rep(c("Target of intervention"), each = condition_size, times = 3), #*3 conditions
  participant = c(rep(seq(from = 1, to = condition_size, by = 1), times = 1),
                  rep(seq(from = condition_size + 1, to = condition_size*2, by = 1), times = 1),
                  rep(seq(from = condition_size*2 + 1, to = condition_size*3, by = 1), times = 1)),
  
  
  # Simulate responses
  response = 
    c(#Internalist (biological): Target of intervention
      sample(c("modify Zarpies biology", "modify Zarpies beliefs/culture", "acquire okinberries", "other"), 
             size = condition_size, 
             replace = TRUE,
             prob = c(0.6, 0.2, 0.1, 0.1)), 
      #Internalist (cultural): Target of intervention
      sample(c("modify Zarpies biology", "modify Zarpies beliefs/culture", "acquire okinberries", "other"), 
             size = condition_size, 
             replace = TRUE,
             prob = c(0.2, 0.6, 0.1, 0.1)), 
      #Structural: Target of intervention
      sample(c("modify Zarpies biology", "modify Zarpies beliefs/culture", "acquire okinberries", "other"), 
             size = condition_size, 
             replace = TRUE,
             prob = c(0.1, 0.1, 0.7, 0.1))) 
  
)
predicted_intervention$response <- predicted_intervention$response %>% 
  factor(levels = c("modify Zarpies biology", "modify Zarpies beliefs/culture", "acquire okinberries", "other"))

# Summarize simulated responses
predicted_summary <- predicted %>% 
  group_by(condition, measure) %>% 
  summarize(avg = mean(response, na.rm = TRUE),
            sd = sd(response, na.rm = TRUE), 
            n = length(unique(participant)))

predicted_intervention_summary <- predicted_intervention %>% 
  group_by(condition, measure) %>% 
  count(response)


# Plot: possibility of change
ggplot(predicted %>% filter(measure == "Possibility of change"), aes(x = condition, y = response)) +
  ggtitle("Possibility of change: predictions") +
  scale_y_continuous(name = "Can Zarpies also eat okinberries?",
                     limits = c(1, 4),
                     # breaks = c(1, 2, 3, 4),
                     labels = c("For sure no: 1", "Maybe no: 2", "Maybe yes: 3", "For sure yes: 4")) +
  geom_hline(yintercept = mean(c(1, 2, 3, 4)), linetype = "dashed") +
  # geom_point(position = position_jitter(width = 0.2, height = 0.05),
  #            size = 2, alpha = 0.1) +
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               color = "gray",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "gray",
               size = 5) 
ggsave("predicted_possibility_change.png")

# Plot: normativity
ggplot(predicted %>% filter(measure == "Normativity"), aes(x = condition, y = response)) +
  ggtitle("Normativity (6-point): predictions") +
    scale_y_continuous(name = "…for this Zarpie to eat okinberries?",
                       limits = c(1, 6),
                       breaks = c(1, 2, 3, 4, 5, 6),
                       labels = c("Very, very good: 1", "Pretty good: 2", "A little good: 3", "A little bad: 4", "Pretty bad: 5", "Very, very bad: 6")) +
  geom_hline(yintercept = mean(c(1, 2, 3, 4, 5, 6)), linetype = "dashed") +
  # geom_point(position = position_jitter(width = 0.2, height = 0.05),
  #            size = 2, alpha = 0.1) +
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               color = "gray",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "gray",
               size = 5) 
ggsave("predicted_normativity.png")


# Plot: target of intervention
ggplot(predicted_intervention, 
       aes(x = condition, fill = response)) +
  geom_bar(position = "fill", alpha = 0.7) +
  guides(fill = guide_legend(title = NULL)) +
  scale_y_continuous(name = "What would you do, so that \n Zarpies can eat okinberies?",
                     labels = scales::percent) +
  scale_fill_manual(values = intervention_colors) + 
  ggtitle("Target of intervention: predictions") 
ggsave("predicted_intervention.png", width = 10)



# Statistical analysis: possibility of change
lm(response ~ condition,
   data = predicted %>% filter(measure == "Possibility of change", condition == "Internalist (biological)" | condition == "Structural")) %>% 
  summary()

# Statistical analysis: normativity
lm(response ~ condition,
   data = predicted %>% filter(measure == "Normativity", condition == "Internalist (biological)" | condition == "Structural")) %>% 
  summary()


# Statistical analysis: target of intervention
# Fix me

```


## Participants

```{r import-data}
# Import pilot data for analysis
data <- read_csv(here("data", "structural-consequences_data_pilot1_coded.csv"))
```

```{r clean-data}
# Filter out those who didn't consent
data <- data %>%
  filter(consent == "I do consent to participate") %>% 
  select(-consent)

# Add participant ID
data <- data %>% 
  mutate(participant = row_number())


# Coalesce redundant columns
data <- data %>% 
  mutate(normativity = coalesce(normativity_notOkay, normativity_okay))

# Keep columns we care about
data <- data %>% 
  select(participant, 
         condition, 
         calibrate_poss_1:normativity_fc,
         normativity,
         intervention_coded:ses
         ) 

# Remove line breaks in responses
data$check_group_berry <- data$check_group_berry %>% 
  str_replace_all("\n", "")
```

```{r exclude}
# Record exclusions
excl <- data %>% 
  summarize(check_group_berry = sum(check_group_berry != "Vawns"),
            check_group = sum(check_group != "Zarpies,Vawns"),
            check_berry = sum(check_berry != "Pogoberries,Okinberries"), 
            check_task = sum(check_task != "Learning about Zarpies and answering questions about them"))

# Exclude participants and remove exclusion columns
data <- data %>%
  filter(check_group_berry == "Vawns" &
           check_group == "Zarpies,Vawns" &
           check_berry == "Pogoberries,Okinberries" &
           check_task == "Learning about Zarpies and answering questions about them") %>% 
  select(-starts_with("check"))


```

```{r sample-size}
# Record number of participants in actual sample after exclusions
n.adults <- data %>% 
  nrow()

# Record number of participants in actual sample per condition
n.adults.condition <- data %>% 
  group_by(condition) %>% 
  summarize(n = length(unique(participant)))
```

```{r dem}
# Record demographics of actual sample
## Age
data$age <- data$age %>% 
  as.numeric()
dem.age <- data %>%
  count(age)

## Gender
dem.gender <- data %>%
  count(gender)

## Race
dem.race <- data %>%
  count(race)

## Education
data$education <- data$education %>% 
  factor(levels = c("Less than high school",
                    "High school/GED",
                    "Some college",
                    "Bachelor's (B.A., B.S.)",
                    "Master's (M.A., M.S.)",
                    "Doctoral (Ph.D., J.D., M.D.)",
                    "Prefer not to specify"))
dem.education <- data %>%
  count(education)

## Socio-economic status (SES) #fixme: Qualtrics renamed labels
data$ses <- data$ses %>% 
  factor(levels = c("Poor",
                    "Working class",
                    "Middle class",
                    "Affluent",
                    "Prefer not to specify"))
dem.ses <- data %>%
  count(ses)

```

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses. 

Participants were excluded for failing the attention checks.
<!-- data cleaning rules, data exclusion rules, covariates, etc. Key analysis of interest. Can also pre-specify additional analyses you plan to do.-->

For the target of intervention question, explanations will be coded into "Internal", "Structural", or "Other" by individuals blind to the research hypothesis. For the purposes of this pilot with adults, explanations will be coded by the experimenter without knowledge of each participant's condition. A fuller coding scheme will be developed before actual testing, but:

- modify Zarpies biology (vaccine, potion, pill, medicine, build tolerance, cross-breed with another alien)
- modify Zarpies beliefs/culture (tell them it's not bad luck, tell them it's good luck, change their thoughts)
- modify okinberries themselves so they are safe to eat (change color, wash them, heat up, cook them, prepare them, remove part, mix with something else, sanitize)
- acquire pogoberries
- acquire okinberries (grow/plant, import, trade, ask Vawns to send, search planet, tell them where to find, share with Vawns, travel, visit Vawns, move to other side of planet, switch spots with Vawns)
- I don't know
- ambiguous (do a magic spell that allows them to eat okinberries, give seeds, ask someone for them, be friendly with others, make it to where the okinberries don't make the Zarpies sick, have it not be poisonous, Will harvest again and cultivate it, establish hospitals for Zarpies when they get sick)
- other (Zarpies will try to eat okinberies, too far away)



- "Internal" = explanations appealing to causes located inside of an individual category member (eg genes, mental states) or inside of the group as a whole (eg culture, shared knowledge)
- "Structural" = explanations appealing to causes located external to the group that operate on the group as a whole (eg location)
- "Other" = idiosyncratic, non-answers, or explanations that appeal to external factors that do not apply to the group as a whole 

```{r recode-tidy}
# Keep columns we care about
data <- data %>% 
  select(participant, 
         condition, 
         possibility_change,
         normativity_fc,
         normativity,
         intervention_coded,
         intervention_diff) 

# Recode dependent measures into numerical values
data$possibility_change <- 
  recode(data$possibility_change,
         "For sure no" = 1,
         "Maybe no" = 2,
         "Maybe yes" = 3,
         "For sure yes" = 4)

data$normativity_fc_coded <- 
  recode(data$normativity_fc,
         "Not okay" = 0,
         "Okay" = 1)

data$normativity <- 
  recode(data$normativity,
         "Very, very good" = 1,
         "Pretty good" = 2,
         "A little good" = 3,
         "A little bad" = 4,
         "Pretty bad" = 5,
         "Very, very bad" = 6)

data$intervention_diff <- 
  recode(data$intervention_diff,
         "Very easy" = 1,
         "Somewhat easy" = 2,
         "Somewhat difficult" = 3,
         "Very difficult" = 4)

# Gather long data to tidy form, and rename
data.tidy <- data %>% 
  gather(measure, response, c("possibility_change", "normativity_fc", "normativity_fc_coded", "normativity", "intervention_coded", "intervention_diff"))

data.tidy$condition <- data.tidy$condition %>% 
  recode("internalist_biological" = "Internalist (biological)",
         "internalist_cultural" = "Internalist (cultural)",
         "structural" = "Structural")

data.tidy$measure <- data.tidy$measure %>% 
  factor(levels = c("possibility_change", "normativity_fc", "normativity_fc_coded", "normativity", "intervention_coded", "intervention_diff"))


# Split out text responses into separate data tables
data.intervention <- data.tidy %>% 
  filter(measure == "intervention_coded" | measure == "intervention_diff") %>% 
  spread(measure, response)
data.tidy <- data.tidy %>% 
  filter(measure != "intervention_coded")

data.intervention$intervention_coded <- data.intervention$intervention_coded %>% 
  factor(levels = c("modify Zarpies biology", 
                    "modify Zarpies beliefs/culture", 
                    "acquire okinberries",
                    "modify okinberries",
                    "acquire pogoberries",
                    "ambiguous",
                    "other",
                    "don't know"))
data.intervention$intervention_diff <- data.intervention$intervention_diff %>% 
  as.numeric()


data.tidy.normativity_fc <- data.tidy %>% 
  filter(measure == "normativity_fc")
data.tidy <- data.tidy %>% 
  filter(measure != "normativity_fc")

data.tidy.normativity_fc$response <- data.tidy.normativity_fc$response %>% 
  factor(levels = c("Okay",
                    "Not okay"))


data.tidy$response <- data.tidy$response %>% 
  as.numeric()

```

# Results
```{r description-visualization}
# Plot responses: possibility of change
ggplot(data.tidy %>% filter(measure == "possibility_change"), 
       aes(x = condition, y = response)) +
  ggtitle("Possibility of change") +
  scale_y_continuous(name = "Can Zarpies also eat okinberries?",
                     breaks = c(1, 2, 3, 4),
                     labels = c("For sure no: 1", "Maybe no: 2", "Maybe yes: 3", "For sure yes: 4")) + 
  geom_hline(yintercept = mean(c(1, 2, 3, 4)), linetype = "dashed") +
  geom_point(position = position_jitter(width = 0.2, height = 0.05),
             size = 2, alpha = 0.1) + 
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5) 
ggsave("possibility_change.png", width = 7)



# Plot: normativity (force choice)
ggplot(data.tidy.normativity_fc, 
       aes(x = condition, fill = response)) +
  geom_bar(position = "fill") +
  geom_hline(yintercept = mean(c(0, 1)), linetype = "dashed") +
  guides(fill = guide_legend(title = "Response")) +
  scale_fill_brewer(type = "div", direction = -1) +
  scale_y_continuous(name = "Attitude towards non-conformity",
                     labels = scales::percent) +
  ggtitle("Normativity (forced choice)") 
ggsave("normativity_fc.png", width = 8)


# Plot responses: normativity
ggplot(data.tidy %>% filter(measure == "normativity"), 
       aes(x = condition, y = response)) +
  ggtitle("Normativity") +
  scale_y_continuous(name = "Attitude towards non-conformity",
                     breaks = c(1, 2, 3, 4, 5, 6),
                     labels = c("Very, very good: 1", "Pretty good: 2", "A little good: 3", "A little bad: 4", "Pretty bad: 5", "Very, very bad: 6")) +
  geom_hline(yintercept = mean(c(1, 2, 3, 4, 5, 6)), linetype = "dashed") +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.1) + 
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5)
ggsave("normativity.png", width = 8)


# Plot: target of intervention
ggplot(data.intervention, 
       aes(x = condition, fill = intervention_coded)) +
  geom_bar(position = "fill") +
  guides(fill = guide_legend(title = NULL)) +
  scale_y_continuous(name = "What would you do, so that \n Zarpies can eat okinberies?",
                     labels = scales::percent) +
  scale_fill_manual(values = intervention_colors) + 
  ggtitle("Target of intervention") 
ggsave("intervention.png", width = 10)


ggplot(data.intervention, 
       aes(x = condition, fill = intervention_coded)) +
  geom_bar(position = "fill") +
  guides(fill = guide_legend(title = NULL)) +
  gghighlight(intervention_coded == "modify Zarpies biology") +
  scale_y_continuous(name = "What would you do, so that \n Zarpies can eat okinberies?",
                     labels = scales::percent) +
  ggtitle("Target of intervention") 
ggsave("intervention.png", width = 10)


# Plot: difficulty of intervention by condition
ggplot(data.intervention, 
       aes(x = condition, y = intervention_diff, color = intervention_coded)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.1) +
  # stat_summary(fun.data = "mean_cl_boot",
  #              position = position_dodge(width = 0.8),
  #              geom = "linerange",
  #              size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5) +
  guides(fill = guide_legend(title = NULL)) +
  scale_y_continuous(name = "How difficult would it be?",
                     labels = c("Very easy: 1", "Somewhat easy: 2", "Somewhat difficult: 3", "Very difficult: 4")) +
  ggtitle("Difficulty of intervention by condition") 
ggsave("intervention_diff_condition.png", width = 10)


# Plot: difficulty of intervention by intervention type
ggplot(data.intervention, 
       aes(x = intervention_coded, y = intervention_diff, color = condition)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.3) +
  # stat_summary(fun.data = "mean_cl_boot",
  #              position = position_dodge(width = 0.8),
  #              geom = "linerange",
  #              size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5) +
  scale_color_manual(values = condition_colors) +
  scale_x_discrete(name = "Target of intervention") +
  scale_y_continuous(name = "How difficult would it be?",
                     labels = c("Very easy: 1", "Somewhat easy: 2", "Somewhat difficult: 3", "Very difficult: 4")) +
  ggtitle("Difficulty of intervention by target of intervention") 
ggsave("intervention_diff.png", width = 18)


```



```{r target-analysis-possibility-change}
# Possibility of change
## Internalist (biological) vs Internalist (cultural)
lm(possibility_change ~ condition + intervention_diff,
   data = data %>% filter(condition == "internalist_biological" | condition == "internalist_cultural")) %>% 
  summary()

fit_possibility_change_1 <- brm(response ~ condition,
                                data = data.tidy %>% filter(measure == "possibility_change", condition == "Internalist (biological)" | condition == "Internalist (cultural)"),
                                save_pars = save_pars(all = TRUE))
fit_possibility_change_2 <- brm(response ~ 1,
                                data = data.tidy %>% filter(measure == "possibility_change", condition == "Internalist (biological)" | condition == "Internalist (cultural)"),
                                save_pars = save_pars(all = TRUE))
bayes_factor(fit_possibility_change_1, fit_possibility_change_2)



## Internalist (cultural) vs Structural
lm(possibility_change ~ condition + intervention_diff,
   data = data %>% filter(condition == "internalist_cultural" | condition == "structural")) %>% 
  summary()

fit_possibility_change_3 <- brm(response ~ condition,
                                data = data.tidy %>% filter(measure == "possibility_change", condition == "Internalist (cultural)" | condition == "Structural"),
                                save_pars = save_pars(all = TRUE))
fit_possibility_change_4 <- brm(response ~ 1,
                                data = data.tidy %>% filter(measure == "possibility_change", condition == "Internalist (cultural)" | condition == "Structural"),
                                save_pars = save_pars(all = TRUE))
bayes_factor(fit_possibility_change_3, fit_possibility_change_4)



## Internalist (biological) vs Structural
lm(possibility_change ~ condition + intervention_diff,
   data = data) %>% 
  summary()

fit_possibility_change_5 <- brm(response ~ condition,
                                data = data.tidy %>% filter(measure == "possibility_change", condition == "Internalist (biological)" | condition == "Structural"),
                                save_pars = save_pars(all = TRUE))
fit_possibility_change_6 <- brm(response ~ 1,
                                data = data.tidy %>% filter(measure == "possibility_change", condition == "Internalist (biological)" | condition == "Structural"),
                                save_pars = save_pars(all = TRUE))
bayes_factor(fit_possibility_change_5, fit_possibility_change_6)


```

```{r target-analysis-normativity}
# Normativity
lm(normativity ~ condition + intervention_diff,
   data = data) %>% 
  summary()

lm(normativity ~ condition + intervention_diff,
   data = data %>% filter(condition == "internalist_biological" | condition == "internalist_cultural")) %>% 
  summary()

lm(normativity ~ condition + intervention_diff,
   data = data %>% filter(condition == "internalist_cultural" | condition == "structural")) %>% 
  summary()

brm(normativity ~ condition + intervention_diff,
   data = data) %>% 
  summary()

fit_normativity_1 <- brm(response ~ condition,
                         data = data.tidy %>% filter(measure == "normativity"),
                         save_pars = save_pars(all = TRUE))
fit_normativity_2 <- brm(response ~ 1,
                         data = data.tidy %>% filter(measure == "normativity"),
                         save_pars = save_pars(all = TRUE))
bayes_factor(fit_normativity_1, fit_normativity_2)

```

```{r exploratory-analysis-all}
# Overall correlations between measures
cor_measures <- cor(data %>% select(possibility_change, normativity, intervention_diff))

cor_measures_sig <- cor.mtest(data %>% select(possibility_change, normativity, intervention_diff), 
                          conf.level = 0.95)

png(height=600, width=600, file="cor_measures.png")
corrplot.mixed(cor_measures, 
               tl.col = "black",
               tl.srt = 45,
               p.mat = cor_measures_sig$p, 
               sig.level = c(0.001, 0.01, 0.05),
               insig = "label_sig",
               pch.cex = 0.9,
               pch.col = "white")
dev.off()
```

```{r exploratory-analysis-possibility_change-intervention_diff}
# Possibility of change and intervention difficulty
## Plot: intervention difficulty by possibility of change
ggplot(data, 
       aes(x = possibility_change, y = intervention_diff)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE, level = 0.95) +
  scale_x_continuous(name = "Possibility of change",
                   breaks = c(1, 2, 3, 4),
                   labels = c("For sure no: 1", "Maybe no: 2", "Maybe yes: 3", "For sure yes: 4")) +
  scale_y_continuous(name = "Difficulty of suggested intervention",
                   breaks = c(1, 2, 3, 4),
                   labels = c("Very easy: 1", "Somewhat easy: 2", "Somewhat difficult: 3", "Very difficult: 4"))
ggsave("intervention_diff_possibility_change.png", width = 8)

ggplot(data, 
       aes(x = possibility_change, y = intervention_diff, color = condition)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE, level = 0.95) +
  scale_color_manual(values = condition_colors) +
  scale_x_continuous(name = "Possibility of change",
                   breaks = c(1, 2, 3, 4),
                   labels = c("For sure no: 1", "Maybe no: 2", "Maybe yes: 3", "For sure yes: 4")) +
  scale_y_continuous(name = "Difficulty of suggested intervention",
                     breaks = c(1, 2, 3, 4),
                     labels = c("Very easy: 1", "Somewhat easy: 2", "Somewhat difficult: 3", "Very difficult: 4"))
ggsave("intervention_diff_possibility_change_condition.png", width = 10)

## Spearman correlation, Kendall correlation (for 2 interval variables)
cor.test(data$possibility_change, data$intervention_diff,  method = "spearman")
cor.test(data$possibility_change, data$intervention_diff,  method = "kendall")
```

```{r exploratory-analysis-possibility_change-normativity}
## Plot: normativity by possibility of change
ggplot(data, 
       aes(x = possibility_change, y = normativity)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE, level = 0.95) +
  scale_x_continuous(name = "Possibility of change",
                   breaks = c(1, 2, 3, 4),
                   labels = c("For sure no: 1", "Maybe no: 2", "Maybe yes: 3", "For sure yes: 4")) +
  scale_y_continuous(name = "Normativity",
                     breaks = c(1, 2, 3, 4, 5, 6),
                     labels = c("Very, very good: 1", "Pretty good: 2", "A little good: 3", "A little bad: 4", "Pretty bad: 5", "Very, very bad: 6"))
ggsave("normativity_possibility_change.png", width = 8)

ggplot(data, 
       aes(x = possibility_change, y = normativity, color = condition)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE, level = 0.95) +
  scale_color_manual(values = condition_colors) +
  scale_x_continuous(name = "Possibility of change",
                   breaks = c(1, 2, 3, 4),
                   labels = c("For sure no: 1", "Maybe no: 2", "Maybe yes: 3", "For sure yes: 4")) +
  scale_y_continuous(name = "Normativity",
                     breaks = c(1, 2, 3, 4, 5, 6),
                     labels = c("Very, very good: 1", "Pretty good: 2", "A little good: 3", "A little bad: 4", "Pretty bad: 5", "Very, very bad: 6"))
ggsave("normativity_possibility_change_condition.png", width = 10)


## Spearman correlation, Kendall correlation (for 2 interval variables)
cor.test(data$possibility_change, data$normativity,  method = "spearman")
cor.test(data$possibility_change, data$normativity,  method = "kendall")

```

```{r exploratory-analysis-normativity_intervention-diff}
## Plot: intervention difficulty by normativity
ggplot(data, 
       aes(x = normativity, y = intervention_diff)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE, level = 0.95) +
  scale_x_continuous(name = "Normativity",
                     breaks = c(1, 2, 3, 4, 5, 6),
                     labels = c("Very, very good: 1", "Pretty good: 2", "A little good: 3", "A little bad: 4", "Pretty bad: 5", "Very, very bad: 6")) +
  scale_y_continuous(name = "Difficulty of suggested intervention",
                     breaks = c(1, 2, 3, 4),
                     labels = c("Very easy: 1", "Somewhat easy: 2", "Somewhat difficult: 3", "Very difficult: 4"))
ggsave("intervention_diff_normativity.png", width = 8)

ggplot(data, 
       aes(x = normativity, y = intervention_diff, color = condition)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE, level = 0.95) +
  scale_color_manual(values = condition_colors) +
  scale_x_continuous(name = "Normativity",
                     breaks = c(1, 2, 3, 4, 5, 6),
                     labels = c("Very, very good: 1", "Pretty good: 2", "A little good: 3", "A little bad: 4", "Pretty bad: 5", "Very, very bad: 6")) +
  scale_y_continuous(name = "Difficulty of suggested intervention",
                     breaks = c(1, 2, 3, 4),
                     labels = c("Very easy: 1", "Somewhat easy: 2", "Somewhat difficult: 3", "Very difficult: 4"))
ggsave("intervention_diff_normativity_condition.png", width = 10)


## Spearman correlation, Kendall correlation (for 2 interval variables)
cor.test(data$normativity, data$intervention_diff,  method = "spearman")
cor.test(data$normativity, data$intervention_diff,  method = "kendall")

```

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
