---
title             : "Consequences of a structural construal for normativity, possibility of change, intervention"
shorttitle        : "Structural consequences"

author: 
  - name          : "Marianna Y. Zhang"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Building 420, 450 Jane Stanford Way, Stanford, CA 94305"
    email         : "marianna.zhang@stanford.edu"

author: 
  - name          : "Ellen M. Markman"
    affiliation   : "1"
    corresponding : no
    address       : "Building 420, 450 Jane Stanford Way, Stanford, CA 94305"
    email         : "markman@stanford.edu"

affiliation:
  - id            : "1"
    institution   : "Stanford University"

authornote: |
Department of Psychology, Stanford University. Thanks to Aarthi Popat for coding the intervention open-ended responses in study one.

abstract: |

We notice that certain categories are more likely than other categories to exhibit particular properties. For instance, relative to other groups in the US, Black people are disproportionately infected by COVID-19, and disproportionately incarcerated. What do we make of such statistical patterns? Observing such group disparities might lead us to wonder "why?" and seek out causal structure. We can generate a loose taxonomy of these potential causal structures by the type of cause they primarily cite. For instance, a structural representation might consider "the cause" of a property to be a cause that is external to the category yet acts on members of the category. Why might a structural representation be different from other representations, and why would we care? Using data from adults and children, I suggest that a structural representation (as opposed to other representations) leads to importantly different beliefs about normativity (what should be the case), the possibility of change (would it be possible for the case to be otherwise), and targets of intervention (if we wanted the case to be otherwise, what should we change). 

<!-- https://tinyurl.com/ybremelq -->

keywords          : "structural thinking, categories, explanation, normativity, possibility of change"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
require("knitr")
#library("papaja")  # not available for R 4.0
library(here)       # setting directory

library(effsize)    # effect sizes for power analysis
library(effectsize) # effect sizes for power analysis
library(pwr)        # power analysis
library(BRRR)       # notify when done

library(psych)      # cohen's kappa for inter-rater reliability

library(MASS, exclude = "select")
library(multcomp)   # multiple pairwise comparisons
library(emmeans)    # multiple pairwise comparisons
library(brglm)      # logistic regression with Firth bias-reduction (when dealing with quasi-complete separation)
library(brms)       # Bayesian mixed effects model
library(tidybayes)  # Bayes factor
library(corrplot)   # correlation plots

library(tidyverse)  # tidying and wrangling data, visualizations
library(ggthemes)   # visualization themes for ggplot2
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r vis-theme, include = FALSE}
# Set visualization theme
theme_set(
  ggthemes::theme_few() +
    theme(text = element_text(size = 16), # large text size for presentation figures
          axis.ticks.x = element_blank()) # remove x-axis ticks
)

condition_colors = c("biological" = "#49808C",
                     "cultural" = "#F2BF80",
                     "structural" = "#D9695F")
```


# Methods
Methods description here

This project's [repository](https://github.com/mariannazhang/structural-consequences) and [preregistration]() can be found online.



## Participants

```{r import-data}
# Import data for analysis
data_raw <- read_csv(here("data", "strConseq_data_pilot3d_coded.csv"))
```

```{r clean-data}
data <- data_raw %>%
  # Filter out those who didn't consent
  filter(consent == "I do consent to participate") %>% 
  
  # Add participant ID, coalesce redundant columns
  mutate(participant = row_number(),
         acceptability_fc = acceptability,
         acceptability = coalesce(acceptability_notOk, acceptability_ok)) %>% 
  
  # Keep columns we care about
  select(participant, 
         condition, 
         starts_with("check"),
         pref_predict,
         acceptability_fc, acceptability,
         diff,
         switched_context,
         expl_rate_1, expl_rate_2, expl_rate_3,
         intervention_coded, intervention_diff,
         age:ses) %>% 
  
  # Renaming columns
  rename(expl_pref = expl_rate_1,
         expl_bestSuited = expl_rate_2,
         expl_constraint = expl_rate_3) %>% 
  
  # Recoding and cleaning
  mutate(condition = condition %>% 
           factor(levels = c("biological_pos",
                             "biological_neg",
                             "cultural_pos",
                             "cultural_neg",
                             "structural")),
         switched_context = switched_context %>% str_replace_all("\n", ""),
         pref_predict = pref_predict %>% recode("For sure no" = 1,
                                                "Likely no" = 2,
                                                "Likely yes" = 3,
                                                "For sure yes" = 4),
         acceptability = acceptability %>% recode("Very, very bad" = 1,
                                                  "Pretty bad" = 2,
                                                  "A little bad" = 3,
                                                  "A little good" = 4,
                                                  "Pretty good" = 5,
                                                  "Very, very good" = 6),
         diff = diff %>% recode("Very similar" = 1,
                                "Somewhat similar" = 2,
                                "Equally similar and different" = 3,
                                "Somewhat different" = 4,
                                "Very different" = 5),
         switched_context = switched_context %>% recode("For sure aquafruit farmer" = 1,
                                                        "Likely aquafruit farmer" = 2,
                                                        "Likely different job" = 3,
                                                        "For sure different job" = 4),
         expl_pref = expl_pref %>% recode("Not at all satisfying" = 1,
                                              "Slightly satisfying" = 2,
                                              "Somewhat satisfying" = 3,
                                              "Very satisfying" = 4,
                                              "Extremely satisfying" = 5),
         expl_bestSuited = expl_bestSuited %>% recode("Not at all satisfying" = 1,
                                              "Slightly satisfying" = 2,
                                              "Somewhat satisfying" = 3,
                                              "Very satisfying" = 4,
                                              "Extremely satisfying" = 5),
         expl_constraint = expl_constraint %>% recode("Not at all satisfying" = 1,
                                              "Slightly satisfying" = 2,
                                              "Somewhat satisfying" = 3,
                                              "Very satisfying" = 4,
                                              "Extremely satisfying" = 5),
         intervention_diff = intervention_diff %>% recode("Very easy" = 1,
                                                          "Somewhat easy" = 2,
                                                          "Somewhat difficult" = 3,
                                                          "Very difficult" = 4),
         age = age %>% as.numeric(),
         education = education %>% factor(
           levels = c(
             "Less than high school",
             "High school/GED",
             "Some college",
             "Bachelor's (B.A., B.S.)",
             "Master's (M.A., M.S.)",
             "Doctoral (Ph.D., J.D., M.D.)",
             "Prefer not to specify")),
         ses = ses %>% factor(levels = c("Poor",
                                         "Working class",
                                         "Middle class",
                                         "Affluent",
                                         "Prefer not to specify")))
```

```{r exclude-sample-size}
# Record exclusions (participants may be counted twice)
sample <- data %>% 
  summarize(check_group = sum(check_group != "Zarpies,Vawns"),
            check_job = sum(check_job != "Aquafruit farmer,Distribution manager"), 
            check_task = sum(check_task != "Learning about Zarpies and answering questions about them"),
            n_collect = n())

# Exclude participants and remove exclusion columns
data <- data %>%
  filter(check_group == "Zarpies,Vawns" &
           check_job == "Aquafruit farmer,Distribution manager" &
           check_task == "Learning about Zarpies and answering questions about them") %>% 
  select(-starts_with("check"))

# Record number of participants in actual sample after exclusions, exclusion rate
sample <- sample %>%  
  mutate(n = nrow(data),
         n_excl = n_collect - n,
         excl_rate = n_excl/n_collect)

# Record number of participants in actual sample per condition
sample_condition <- data %>% 
  group_by(condition) %>% 
  summarize(n = length(unique(participant)))
```
We excluded `r sample$n_excl `participants (or `r sample$excl_rate` of all participants) based on pre-planned exclusion criteria.

After exclusions, we retained `r sample$n` participants: `r sample_condition$biological` in the biological condition, `r sample_condition$cultural` in the cultural condition, and `r sample_condition$structural` in the structural condition.

```{r dem}
# Record demographics of actual sample
## Age
dem_age <- data %>%
  count(age)

## Gender
dem_gender <- data %>%
  count(gender, sort = TRUE) %>% 
  mutate(prop = n/sample$n)

## Race
dem_race <- data %>%
  count(race, sort = TRUE) %>% 
  mutate(prop = n/sample$n)

## Education
dem_education <- data %>%
  count(education) %>% 
  mutate(prop = n/sample$n)

## Socio-economic status (SES) 
dem_ses <- data %>%
  count(ses) %>% 
  mutate(prop = n/sample$n)

```

## Material

## Procedure



## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses. 

Participants were excluded for failing the attention checks.
<!-- data cleaning rules, data exclusion rules, covariates, etc. Key analysis of interest. Can also pre-specify additional analyses you plan to do.-->


```{r}
# Dummy variables for target of intervention codes
data_intervention <- data %>% 
  mutate(intervention_coded = intervention_coded %>% 
           str_replace_all(" ", "_") %>%
           str_replace_all("/", "_") %>%
           str_replace_all("'", "")) %>% 
  mutate(counts = 1) %>%
  spread(intervention_coded, counts, fill = 0)
```

```{r}
# Gather long data to tidy form, and rename
data_tidy <- data %>% 
  gather(measure, response, 
         c(pref_predict,
           acceptability_fc, acceptability,
           diff, 
           switched_context,
           expl_pref, expl_bestSuited, expl_constraint,
           intervention_coded, intervention_diff)) %>% 
  mutate(measure = measure %>% factor(levels = c("pref_predict",
                                                 "acceptability_fc", "acceptability",
                                                 "diff", 
                                                 "expl_pref", "expl_bestSuited", "expl_constraint",
                                                 "intervention_coded", "intervention_diff")))

# Split out open-ended text responses
data_tidy_intervention <- data_tidy %>% 
  filter(measure == "intervention_coded" | measure == "intervention_diff") %>% 
  spread(measure, response) %>% 
  mutate(intervention_coded = intervention_coded %>% 
           factor(levels = c("target group biology",
                             "provide job tools to group",
                             "provide job training to group",
                             "change group beliefs/culture",
                             "create more jobs or access to jobs", 
                             "change job wages or value",
                             "change job conditions",
                             "other",
                             "ambiguous",
                             "don't know")),
         intervention_diff = intervention_diff %>% as.numeric())

# Split out forced choice responses
data_tidy_fc <- data_tidy %>% 
  filter(measure == "acceptability_fc") %>% 
  mutate(response = response %>% factor(levels = c("Okay",
                                                   "Not okay")))

# Remove those responses from data_tidy, and format responses as numeric
data_tidy <- data_tidy %>% 
  filter(measure != "intervention_coded" &
           measure != "acceptability_fc") %>% 
  mutate(response = response %>% as.numeric())
```


# Results
## Tables
```{r description}
# calculate means and sds by condition
summary_stats <- data %>% 
  group_by(condition) %>% 
  summarize(pref_predict_mean = mean(pref_predict, na.rm = TRUE),
            pref_predict_sd = sd(pref_predict, na.rm = TRUE),
            acceptability_mean = mean(acceptability, na.rm = TRUE),
            acceptability_sd = sd(acceptability, na.rm = TRUE),
            diff_mean = mean(diff, na.rm = TRUE),
            diff_sd = sd(diff, na.rm = TRUE),
            switched_context_mean = mean(switched_context, na.rm = TRUE),
            switched_context_sd = sd(switched_context, na.rm = TRUE),
            expl_pref_mean = mean(expl_pref, na.rm = TRUE),
            expl_pref_sd = sd(expl_pref, na.rm = TRUE),
            expl_bestSuited_mean = mean(expl_bestSuited, na.rm = TRUE),
            expl_bestSuited_sd = sd(expl_bestSuited, na.rm = TRUE),
            expl_constraint_mean = mean(expl_constraint, na.rm = TRUE),
            expl_constraint_sd = sd(expl_constraint, na.rm = TRUE))
summary_stats


# make contingency table of intervention responses
# fixme
data_intervention_counts <- data_intervention %>% 
  group_by(condition) %>% 
  summarize(across(target_group_biology,
                   provide_job_training_to_group,
                   change_group_beliefs_culture,
                   create_more_jobs_or_access_to_jobs,
                   change_job_conditions,
                   change_job_wages_or_value,
                   other,
                   ambiguous,
                   dont_know), ~sum(.))

```

## Plots
### Preference prediction
```{r description-visualization}
# Plot responses: preference prediction
ggplot(data, aes(x = condition, y = pref_predict)) +
  ggtitle("A group member who wants to work the other job") +
  scale_y_continuous(name = "How likely is it that they actually do become a dist manager?",
                     limits = c(1, 4),
                     breaks = c(1, 2, 3, 4),
                     labels = c("For sure no: 1", "Likely no: 2", "Likely yes: 3", "For sure yes: 4")) + 
  geom_hline(yintercept = mean(c(1, 2, 3, 4)), linetype = "dashed") +
  geom_point(position = position_jitter(width = 0.2, height = 0.1),
             size = 2, alpha = 0.1) + 
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5) 
ggsave("pref_predict.png", width = 15)

```

### Acceptability
```{r}
# Plot responses: acceptability
ggplot(data, aes(x = condition, y = acceptability)) +
  ggtitle("Acceptability") +
  scale_y_continuous(name = "attitudes towards current group patterns",
                     breaks = c(1, 2, 3, 4, 5, 6),
                     labels = c("very, very bad", "pretty bad", "a little bad", "a little good", "pretty good", "very, very good")) +
  geom_hline(yintercept = mean(c(1, 2, 3, 4, 5, 6)), linetype = "dashed") +
  geom_point(position = position_jitter(width = 0.2, height = 0.1),
             size = 2, alpha = 0.1) + 
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5)
ggsave("acceptability.png", width = 15)

```

### Switched context
```{r}
# Plot responses: switched context
ggplot(data, aes(x = condition, y = switched_context)) +
  ggtitle("Switched context",
          "born, raised, lives in a different island country") +
  scale_y_continuous(name = "a group member outside context",
                     limits = c(1, 4),
                     breaks = c(1:4),
                     labels = c("for sure aquafruit farmer", "probably aquafruit farmer", "probably diff job", "for sure diff job")) +
  geom_hline(yintercept = mean(1:4), linetype = "dashed") +
  geom_point(position = position_jitter(width = 0.2, height = 0.1),
             size = 2, alpha = 0.1) + 
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5)
ggsave("switched_context.png", width = 8)

```

### Group differences
```{r group-diff}
# Plot responses: group differences
ggplot(data, aes(x = condition, y = diff)) +
  ggtitle("Group differences") +
  scale_y_continuous(name = "Zarpies and Vawns are...",
                     limits = c(1, 5),
                     breaks = c(1, 2, 3, 4, 5),
                     labels = c("Very similar", "Somewhat similar", "Equally similar and different", "Somewhat different", "Very different")) +
  geom_hline(yintercept = mean(c(1, 2, 3, 4, 5)), linetype = "dashed") +
  geom_point(position = position_jitter(width = 0.2, height = 0.1),
             size = 2, alpha = 0.1) + 
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5)
ggsave("group_diff.png", width = 8)

```
### Explanation ratings
```{r expl-pref}
# Plot responses: explanation ratings: preference
ggplot(data, aes(x = condition, y = expl_pref)) +
  ggtitle("Rate: Zarpies prefer to work as aquafruit farmers.") +
  scale_y_continuous(name = "How satisfying?",
                     limits = c(1, 5),
                     breaks = c(1:5),
                     labels = c("Not at all", "Slightly", "Somewhat", "Very", "Extremely")) +
  geom_point(position = position_jitter(width = 0.2, height = 0.1),
             size = 2, alpha = 0.1) + 
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5)
ggsave("expl_pref.png", width = 8)

```
```{r expl-bestSuited}
# Plot responses: explanation ratings: best suited
ggplot(data, aes(x = condition, y = expl_bestSuited)) +
  ggtitle("Rate: Zarpies are best-suited to working as aquafruit farmers.") +
  scale_y_continuous(name = "How satisfying?",
                     limits = c(1, 5),
                     breaks = c(1:5),
                     labels = c("Not at all", "Slightly", "Somewhat", "Very", "Extremely")) +
  geom_point(position = position_jitter(width = 0.2, height = 0.1),
             size = 2, alpha = 0.1) + 
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5)
ggsave("expl_bestSuited.png", width = 8)

```

```{r expl-constraint}
# Plot responses: explanation ratings: constraint
ggplot(data, aes(x = condition, y = expl_constraint)) +
  ggtitle("Rate: Zarpies have few other options than to be aquafruit farmers.") +
  scale_y_continuous(name = "How satisfying?",
                     limits = c(1, 5),
                     breaks = c(1:5),
                     labels = c("Not at all", "Slightly", "Somewhat", "Very", "Extremely")) +
  geom_point(position = position_jitter(width = 0.2, height = 0.1),
             size = 2, alpha = 0.1) + 
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5)
ggsave("expl_constraint.png", width = 8)

```

### Target of intervention
```{r target-of-intervention}
# Plot: target of intervention
ggplot(data_tidy_intervention, 
       aes(x = condition, fill = intervention_coded)) +
  ggtitle("Target of intervention") +
  geom_bar(position = "fill") +
  scale_fill_manual(values = intervention_colors) +
  guides(fill = guide_legend(title = NULL)) +
  scale_y_continuous(name = "What would you do, so that \n Zarpies can work as distribution managers?",
                     labels = scales::percent,
                     expand = c(0,0)) +
  scale_x_discrete(expand = c(0,0))
ggsave("intervention.png", width = 10)

```

### Difficulty of intervention
```{r}
# Plot: difficulty of intervention by condition
ggplot(data_tidy_intervention, 
       aes(x = condition, y = intervention_diff, color = intervention_coded)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5) +
  guides(fill = guide_legend(title = NULL)) +
  scale_y_continuous(name = "How difficult would it be?",
                     labels = c("Very easy: 1", "Somewhat easy: 2", "Somewhat difficult: 3", "Very difficult: 4")) +
  ggtitle("Difficulty of intervention by condition") 
ggsave("intervention_diff_condition.png", width = 10)


# Plot: difficulty of intervention by intervention type
ggplot(data_tidy_intervention, 
       aes(x = intervention_coded, y = intervention_diff, color = condition)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.3) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5) +
  scale_color_manual(values = condition_colors) +
  scale_x_discrete(name = "Target of intervention") +
  scale_y_continuous(name = "How difficult would it be?",
                     labels = c("Very easy: 1", "Somewhat easy: 2", "Somewhat difficult: 3", "Very difficult: 4")) +
  ggtitle("Difficulty of intervention by target of intervention") 
ggsave("intervention_diff.png", width = 18)
```

## Power analysis for later study

```{r power-analysis-bootstrap-pairwise, eval = FALSE, warnings = FALSE}
# Import pilot data, with measure adjustments since pilot
data_pilot <- data %>% 
  filter(condition == "biological_pos" | condition == "cultural_pos" | condition == "structural") %>% 
  mutate(condition = condition %>% recode(
    "biological_pos" = "biological",
    "cultural_pos" = "cultural",
    "structural" = "structural"))

# set parameters
alpha <- 0.05 # p-value criterion

contrasts <- lm(acceptability ~ condition + intervention_diff, 
                data = data_pilot) %>% 
  emmeans("condition") %>% 
  pairs() %>% 
  summary() %>% 
  pull(contrast) # condition comparisons

simulations <- 300


# set up simulation grid
power <- crossing(
  alpha = alpha,
  sample_size = c(20, 30, 40, 50, 60), 
  simulation = rep(1:simulations, 5) # __ simulations per each of 5 possible ns
)


# create a function to sample from pilot data and run analyses on the resample
bootstrap_analysis <- function(sample_size, alpha = 0.05, simulation = NULL){
  # resample sample_size # of participants from pilot data (bootstrap)
  resample <- bind_rows(data_pilot %>% 
                          filter(condition == "biological") %>% 
                          slice_sample(n = sample_size, replace = TRUE),
                        data_pilot %>% 
                          filter(condition == "cultural") %>% 
                          slice_sample(n = sample_size, replace = TRUE),
                        data_pilot %>% 
                          filter(condition == "structural") %>% 
                          slice_sample(n = sample_size, replace = TRUE)) %>% 
    mutate(observation = row_number())
  
  
  # dummy columns for target of intervention responses
  resample$intervention_coded <- resample$intervention_coded %>% 
    str_replace_all(" ", "_") %>% 
    str_replace_all("/", "_") 
  
  resample <- resample %>% 
    mutate(counts = 1) %>%
    spread(intervention_coded, counts, fill = 0)
  
  
  # run analysis (brglm in case separation in logistic regression), pull p-values
  results <- tibble(
    contrast = contrasts,
    acceptability = lm(acceptability ~ condition + intervention_diff, 
                            data = resample) %>% 
      emmeans("condition") %>% 
      pairs(adjust = "fdr") %>% 
      summary() %>% 
      pull(p.value),
    diff = lm(diff ~ condition + intervention_diff, 
                     data = resample) %>% 
      emmeans("condition") %>%
      pairs(adjust = "fdr") %>% 
      summary() %>% 
      pull(p.value),
    switched_context = lm(switched_context ~ condition + intervention_diff, 
                     data = resample) %>% 
      emmeans("condition") %>%
      pairs(adjust = "fdr") %>% 
      summary() %>% 
      pull(p.value),
    
    expl_pref = lm(expl_pref ~ condition + intervention_diff, 
                     data = resample) %>% 
      emmeans("condition") %>%
      pairs(adjust = "fdr") %>% 
      summary() %>% 
      pull(p.value),
    
    expl_bestSuited = lm(expl_bestSuited ~ condition + intervention_diff, 
                     data = resample) %>% 
      emmeans("condition") %>%
      pairs(adjust = "fdr") %>% 
      summary() %>% 
      pull(p.value),
    
    expl_constraint = lm(expl_constraint ~ condition + intervention_diff, 
                     data = resample) %>% 
      emmeans("condition") %>%
      pairs(adjust = "fdr") %>% 
      summary() %>% 
      pull(p.value),
    
    # provide_job_training_to_group = brglm(provide_job_training_to_group ~ condition + intervention_diff,
    #                              family = "binomial",
    #                              data = resample) %>% 
    #   emmeans("condition") %>% 
    #   pairs(adjust = "fdr") %>% 
    #   summary() %>% 
    #   pull(p.value),
    # change_group_beliefs_culture = brglm(change_group_beliefs_culture ~ condition + intervention_diff,
    #                              family = "binomial",
    #                              data = resample) %>% 
    #   emmeans("condition") %>% 
    #   pairs(adjust = "fdr") %>% 
    #   summary() %>% 
    #   pull(p.value),
    # create_more_jobs_or_access_to_jobs = brglm(create_more_jobs_or_access_to_jobs ~ condition + intervention_diff,
    #                              family = "binomial",
    #                              data = resample) %>% 
    #   emmeans("condition") %>% 
    #   pairs(adjust = "fdr") %>% 
    #   summary() %>% 
    #   pull(p.value),
    # change_job_wages_or_value = brglm(change_job_wages_or_value ~ condition + intervention_diff,
    #                              family = "binomial",
    #                              data = resample) %>% 
    #   emmeans("condition") %>% 
    #   pairs(adjust = "fdr") %>% 
    #   summary() %>% 
    #   pull(p.value)
    )
  
  return(results)
}

# run the bootstrap analysis function over the whole grid, using the different sample sizes specified
power_exp <- power %>% 
  mutate(results = pmap(power, bootstrap_analysis)) %>% 
  unnest()


# calculate the proportion with which the H0 would be rejected (= power), under the different sample sizes specified
power_results <- power_exp %>% 
  group_by(sample_size, contrast) %>%
  summarize(acceptability = sum(acceptability < .05) / n(),
            diff = sum(diff < .05) / n(),
            switched_context = sum(switched_context < .05) / n(),
            expl_pref = sum(expl_pref < .05) / n(),
            expl_bestSuited = sum(expl_bestSuited < .05) / n(),
            expl_constraint = sum(expl_constraint < .05) / n(),
            # provide_job_training_to_group = sum(provide_job_training_to_group < .05) / n(),
            # change_group_beliefs_culture = sum(change_group_beliefs_culture < .05) / n(),
            # create_more_jobs_or_access_to_jobs = sum(create_more_jobs_or_access_to_jobs < .05) / n(),
            # change_job_wages_or_value = sum(change_job_wages_or_value < .05) / n()
            )
power_results
write.csv(power_results, file = "power_results.csv")

skrrrahh(26) # notify when done

```

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
