---
title             : "Consequences of a structural construal for generalization, normativity, possibility of change, intervention"
shorttitle        : "Structural consequences"

author: 
  - name          : "Marianna Y. Zhang"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Building 420, 450 Jane Stanford Way, Stanford, CA 94305"
    email         : "marianna.zhang@stanford.edu"

author: 
  - name          : "Ellen M. Markman"
    affiliation   : "1"
    corresponding : no
    address       : "Building 420, 450 Jane Stanford Way, Stanford, CA 94305"
    email         : "markman@stanford.edu"

affiliation:
  - id            : "1"
    institution   : "Stanford University"

authornote: |
Department of Psychology, Stanford University. Thanks to Aarthi Popat for coding the intervention open-ended responses in study one.

abstract: |

We notice that certain categories are more likely than other categories to exhibit particular properties. For instance, relative to other groups in the US, Black people are disproportionately infected by COVID-19, and disproportionately incarcerated. What do we make of such statistical patterns? Observing such group disparities might lead us to wonder "why?" and seek out causal structure. We can generate a loose taxonomy of these potential causal structures by the type of cause they primarily cite. For instance, a structural representation might consider "the cause" of a property to be a cause that is external to the category yet acts on members of the category. Why might a structural representation be different from other representations, and why would we care? Using data from adults and children, I suggest that a structural representation (as opposed to other representations) leads to importantly different beliefs about normativity (what should be the case), the possibility of change (would it be possible for the case to be otherwise), and targets of intervention (if we wanted the case to be otherwise, what should we change). 

<!-- https://tinyurl.com/ybremelq -->

keywords          : "structural thinking, categories, explanation, normativity, possibility of change"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
require("knitr")
#library("papaja")  # not available for R 4.0
library(readxl)     # import data from Excel
library(here)       # setting directory

library(MASS, exclude = "select")
library(effsize)    # effect sizes for power analysis
library(effectsize) # effect sizes for power analysis
library(pwr)        # power analysis
library(BRRR)       # notify when done

library(psych)      # cohen's kappa for inter-rater reliability

library(multcomp)   # multiple pairwise comparisons
library(emmeans)    # multiple pairwise comparisons
library(brglm)      # logistic regression with Firth bias-reduction (when dealing with quasi-complete separation)
library(brms)       # Bayesian mixed effects model
library(tidybayes)  # Bayes factor

library(corrplot, exclude = "select")   # correlation plots

library(tidyverse)  # tidying and wrangling data, visualizations
library(ggthemes)   # visualization themes for ggplot2
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r vis-theme, include = FALSE}
# Set visualization theme
theme_set(
  ggthemes::theme_few() +
    theme(text = element_text(size = 16), # large text size for presentation figures
          axis.ticks.x = element_blank()) # remove x-axis ticks
)

intervention_codes <- c(
  "modify group biology",
  "modify group beliefs/culture",
  "modify environment",
  "modify berry",
  "acquire original berry",
  "other",
  "ambiguous",
  "don't know"
)

intervention_codes_clean <- intervention_codes %>% 
  str_replace_all(" ", "_") %>% 
  str_replace_all("/", "_") %>% 
  str_replace_all("'", "")

intervention_colors <- c(
  "modify group biology" = "#D9695F",
  "modify group beliefs/culture" = "#F2BF80",
  "modify environment" = "#49808C",
  "modify berry" = "#D9BAB7",
  "acquire original berry" = "#C3C7B6",
  "other" = "#D9D9D9",
  "ambiguous" = "#D9D9D9",
  "don't know" = "#D9D9D9"
  # "don't know" = "#9E9E9E"
)


intervention_colors_highlight <- c(
  "modify group biology" = "#D9BAB7",
  "modify group beliefs/culture" = "#D9BAB7",
  "modify environment" = "#49808C",
  "modify berry" = "#D9D9D9",
  "acquire original berry" = "#D9D9D9",
  "other" = "#D9D9D9",
  "ambiguous" = "#D9D9D9",
  "don't know" = "#D9D9D9"
  # "don't know" = "#9E9E9E"
)

condition_colors <- c(
  "biological" = "#D9695F",
  "cultural" = "#F2BF80",
  "structural" = "#49808C"
)
```


# Methods
This project's [repository](https://github.com/mariannazhang/structural-consequences) can be found online.


## Participants

```{r import-data}
# Import data for analysis
data_raw <- read_excel(here("data", "strConseq_data_study2.xlsx"), sheet = 1)
```

```{r clean-exclude-sample}
# Keep columns we care about
data <- data_raw %>% 
  select(-file, -test_date:-onlineTesting_id,
         -intervention,
         -consent:-comments,
         -ends_with("comments"))

# Record exclusions (participants may be counted twice) & exclusion rate
sample <- data %>% 
  summarize(atypical = sum(atypical != "no"),
            out_of_age = sum(out_of_age != "no"),
            exp_error = sum(exp_error != "no"),
            interference = sum(interference != "no"), 
            insuff_lang = sum(insuff_lang != "no"),
            n_excl = sum(exclude == "yes"),
            n_run = n()) %>%
  mutate(excl_rate = round(n_excl/n_run, 3)) # exclusion rate, rounded to 3 decimal points

# Exclude participants and remove exclusion columns
data <- data %>%
  filter(exclude == "no") %>% 
  select(-exclude:-insuff_lang)

# Record number of participants in actual sample after exclusions
sample <- sample %>%
  mutate(n = nrow(data)) # actual sample size

# Record number of participants in actual sample per condition
n.condition <- data %>% 
  group_by(condition) %>% 
  summarize(n = length(unique(participant)))
```
We excluded `r sample$n_excl `participants (or `r sample$excl_rate` of all participants) based on pre-planned exclusion criteria.

After exclusions, we retained `r sample$n` participants: `r n.condition$biological` in the biological condition, `r n.condition$cultural` in the cultural condition, and `r n.condition$structural` in the structural condition.

```{r dem}
# Record demographics of actual sample
## Age
dem_age <- data %>%
  count(age_cat)

## Gender
dem_gender <- data %>% 
  count(gender, sort = TRUE) %>% 
  mutate(prop = n/sample$n)

## Race
dem_race <- data %>%
  count(race, sort = TRUE) %>% 
  mutate(prop = n/sample$n)

```

## Material

## Procedure


For the target of intervention question, explanations will be coded by 2 coders blind to condition, using the following coding scheme: 

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses. 

Participants were excluded for failing the attention checks.
<!-- data cleaning rules, data exclusion rules, covariates, etc. Key analysis of interest. Can also pre-specify additional analyses you plan to do.-->


```{r recode-tidy}
# Recode dependent measures into numerical values
data <- data %>% 
  mutate(possibility_change = possibility_change %>% 
           recode("for sure no" = 1,
                  "no" = 1.5,
                  "maybe no" = 2,
                  "maybe yes" = 3,
                  "yes" = 3.5,
                  "for sure yes" = 4),
         switched_context = 
           if_else(cb_berry == "starRound", 
                   (recode(switched_context,
                           "for sure starberries" = 1,
                           "maybe starberries" = 2,
                           "maybe roundberries" = 3,
                           "for sure roundberries" = 4)),
                   (recode(switched_context,
                           "for sure roundberries" = 1,
                           "maybe roundberries" = 2,
                           "maybe starberries" = 3,
                           "for sure starberries" = 4))),
         normativity = normativity %>% 
           recode("very good" = 1,
                  "pretty good" = 2,
                  "a little good" = 3,
                  "a little bad" = 4,
                  "pretty bad" = 5,
                  "very bad" = 6),
         intervention_coded = intervention_coded %>% 
           factor(),
         intervention_diff = intervention_diff %>% 
           recode("very easy" = 1,
                  "easy" = 1.5,
                  "a little easy" = 2,
                  "a little hard" = 3,
                  "hard" = 3.5,
                  "very hard" = 4))
```

```{r interrater-reliability}
# Calculate inter-rater reliability for intervention coding: % agreement, and Cohen's kappa
data <- data %>%
  mutate(intervention_coded_same = (intervention_coded_1 == intervention_coded_2))

intervention_reliability <- data %>%
  summarize(percent_agreement =
              sum(intervention_coded_same) / length(intervention_coded_same))

intervention_reliability <- intervention_reliability %>%
  mutate(cohen_kappa = cohen.kappa(x = data %>%
                                     select(intervention_coded_1,
                                            intervention_coded_2) %>%
                                     as.data.frame())$kappa)

# Remove individual coder columns
data <- data %>%
  select(-intervention_coded_1, -intervention_coded_2, -intervention_coded_same)
```
Inter-rater reliability on coding intervention responses was high (`r intervention_reliability$percent_agreement` agreement, `r intervention_reliability$cohen_kappa` Cohen's kappa).

```{r intervention}
# Split off target of intervention
data_intervention <- data %>% 
  mutate(
    # Cleaning
    intervention_coded = intervention_coded %>% 
      str_replace_all(" ", "_") %>% 
      str_replace_all("/", "_") %>% 
      str_replace_all("'", "") %>% 
      factor(intervention_codes_clean),
    # Add dummy variable for spreading
    counts = 1) %>% 
  # Add any missing intervention code values, keeping all other columns the same (workaround for spread(drop = FALSE))
  complete(nesting(!!!select(., participant:switched_context, intervention_diff)), intervention_coded) %>% 
  # Spread
  spread(intervention_coded, counts, fill = 0)
```

```{r tidy-cleaning-splitoff}
# Create tidy data
data_tidy <- data %>% 
  # tidy
  gather(measure, response, 
         c("possibility_change_fc", "possibility_change", 
           "normativity_fc", "normativity", 
           "switched_context_fc", "switched_context",
           "intervention_coded", "intervention_diff")) %>% 
  # cleaning
  mutate(measure = measure %>% 
           factor(levels = c("possibility_change_fc", "possibility_change", 
                             "normativity_fc", "normativity", 
                             "switched_context_fc", "switched_context",
                             "intervention_coded", "intervention_diff")))

# Split out intervention
data_tidy_intervention <- data_tidy %>% 
  filter(measure == "intervention_coded" | measure == "intervention_diff") %>% 
  spread(measure, response) %>% 
  mutate(intervention_coded = intervention_coded %>% 
           factor(levels = intervention_codes),
         intervention_diff =intervention_diff %>% 
           as.numeric())

# Split out forced choice measures
data_tidy_fc <- data_tidy %>% 
  filter(measure == "possibility_change_fc" | 
           measure == "normativity_fc" | 
           measure == "switched_context_fc")

# Remove split off measures from data_tidy, and format responses as numeric
data_tidy <- data_tidy %>% 
  filter(measure != "intervention_coded" &
           measure != "possibility_change_fc" & 
           measure != "normativity_fc" &
           measure != "switched_context_fc") %>% 
  mutate(response = response %>% 
           as.numeric())
```


# Results
## Tables
```{r description}
# calculate means and sds by condition
summary_stats <- data %>% 
  group_by(condition) %>% 
  summarize(possibility_change_mean = mean(possibility_change, na.rm = TRUE),
            possibility_change_sd = sd(possibility_change, na.rm = TRUE),
            normativity_mean = mean(normativity, na.rm = TRUE),
            normativity_sd = sd(normativity, na.rm = TRUE),
            switched_context_mean = mean(switched_context, na.rm = TRUE),
            switched_context_sd = sd(switched_context, na.rm = TRUE))
summary_stats


# make contingency table of intervention responses
data_intervention_counts <- data_intervention %>% 
  group_by(condition) %>% 
  summarize(modify_group_biology = sum(modify_group_biology),
            modify_group_beliefs_culture = sum(modify_group_beliefs_culture),
            modify_environment = sum(modify_environment),
            modify_berry = sum(modify_berry),
            acquire_original_berry = sum(acquire_original_berry),
            ambiguous = sum(ambiguous),
            dont_know = sum(dont_know))

```

## Plots
### Possibility of change
```{r possibility-change}
# Plot responses: possibility of change
ggplot(data, 
       aes(x = condition, y = possibility_change)) +
  # ggtitle("Possibility of change") +
  scale_y_continuous(name = "",
                     # name = "Can Zarpies also eat roundberries?",
                     limits = c(0.9, 4.1),
                     breaks = c(1, 2, 3, 4),
                     labels = c("for sure no", "maybe no", "maybe yes", "for sure yes")) + 
  geom_hline(yintercept = mean(c(1, 2, 3, 4)), linetype = "dashed") +
  geom_point(position = position_jitter(width = 0.2, height = 0.05),
             size = 2, alpha = 0.1) + 
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5) 
ggsave("possibility_change.png", width = 7)


# Blank
ggplot(data, 
       aes(x = condition, y = possibility_change)) +
  # ggtitle("Possibility of change") +
  scale_y_continuous(name = "",
                     limits = c(0.9, 4.1),
                     breaks = c(1, 2, 3, 4),
                     labels = c("for sure no", "maybe no", "maybe yes", "for sure yes")) + 
  scale_x_discrete(limits = c("biological", "cultural", "structural")) +
  geom_hline(yintercept = mean(c(1, 2, 3, 4)), linetype = "dashed") 
ggsave("possibility_change_blank.png", width = 7)

```

### Normativity
```{r normativity}
# Plot responses: normativity
ggplot(data, aes(x = condition, y = normativity)) +
  # ggtitle("Normativity") +
  scale_y_reverse(name = "",
                     breaks = c(1, 2, 3, 4, 5, 6),
                     labels = c("very good", "pretty good", "a little good", "a little bad", "pretty bad", "very bad")) +
  geom_hline(yintercept = mean(c(1, 2, 3, 4, 5, 6)), linetype = "dashed") +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.1) + 
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5)
ggsave("normativity.png", width = 7)


# Blank
ggplot(data, aes(x = condition, y = normativity)) +
  # geom_point() +
  scale_y_reverse(name = "",
                  limits = c(6, 1),
                  breaks = c(1:6),
                  labels = c("very good", "pretty good", "a little good", "a little bad", "pretty bad", "very bad")) +
  geom_hline(yintercept = mean(c(1:6)), linetype = "dashed") +
  scale_x_discrete(limits = c("biological", "cultural", "structural"))
ggsave("normativity_blank.png", width = 7)
```

```{r normativity-age}
# Plot responses: normativity by age
ggplot(data, 
       aes(x = age, y = normativity)) +
  facet_wrap(vars(condition)) +
  # ggtitle("Normativity") +
  scale_y_reverse(name = "Individual non-conformity",
                     limits = c(6.1, 0.9),
                     breaks = c(1:6),
                     labels = c("very good", "pretty good", "a little good", "a little bad", "pretty bad", "very bad")) +
  geom_hline(yintercept = mean(c(1:6)), linetype = "dashed") +
  geom_point(size = 2, alpha = 0.8) + 
  geom_smooth()
ggsave("normativity_age.png")
```

### Switched context
```{r}
# Plot responses: switched context
ggplot(data, aes(x = condition, y = switched_context)) +
  # ggtitle("Switched context") +
  scale_y_continuous(name = "",
                     # name = "Prediction about member outside context",
                     breaks = c(1, 2, 3, 4),
                     labels = c("for sure [same berry]", "maybe [same berry]", "maybe [other berry]", "for sure [other berry]")) +
  geom_hline(yintercept = mean(c(1, 2, 3, 4)), linetype = "dashed") +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.1) + 
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5)
ggsave("switched_context.png", width = 7)


# Blank
ggplot(data, aes(x = condition, y = switched_context)) +
  # ggtitle("Switched context") +
  scale_y_continuous(name = "",
                     # name = "Prediction about member outside context",
                     limits = c(0.9, 4.1),
                     breaks = c(1, 2, 3, 4),
                     labels = c("for sure [same berry]", "maybe [same berry]", "maybe [other berry]", "for sure [other berry]")) +
  geom_hline(yintercept = mean(c(1, 2, 3, 4)), linetype = "dashed") +
  scale_x_discrete(limits = c("biological", "cultural", "structural"))
ggsave("switched_context_blank.png", width = 7)

```

```{r vis-switched-context-age}
# Plot responses: switched context by age
ggplot(data, 
       aes(x = age, y = switched_context)) +
  facet_wrap(vars(condition)) +
  ggtitle("Switched context") +
  scale_y_continuous(name = "Prediction about member outside context",
                     breaks = c(1, 2, 3, 4),
                     labels = c("For sure [same berry]", "Maybe [same berry]", "Maybe [other berry]", "For sure [other berry]")) +
  geom_hline(yintercept = mean(c(1, 2, 3, 4)), linetype = "dashed") +
  geom_point(size = 2, alpha = 0.8) + 
  geom_smooth()
ggsave("switched_context_age.png")
```

### Target of intervention
```{r plot-intervention}
# Plot: target of intervention
ggplot(data_tidy_intervention, 
       aes(x = condition, fill = intervention_coded)) +
  # ggtitle("Target of intervention") 
  geom_bar(position = "fill") +
  guides(fill = guide_legend(title = NULL)) +
  scale_y_continuous(name = "",
                     # name = "What would you do, so that \n Zarpies can eat roundberries?",
                     labels = scales::percent,
                     expand = c(0,0)) +
  scale_x_discrete(expand = c(0,0)) +
  scale_fill_manual(values = intervention_colors) 
ggsave("intervention.png", width = 10)


# Plot: target of intervention
ggplot(data_tidy_intervention, 
       aes(x = condition, fill = intervention_coded)) +
  # ggtitle("Target of intervention") 
  geom_bar(position = "fill") +
  guides(fill = guide_legend(title = NULL)) +
  scale_y_continuous(name = "",
                     # name = "What would you do, so that \n Zarpies can eat roundberries?",
                     labels = scales::percent,
                     expand = c(0,0)) +
  scale_x_discrete(expand = c(0,0)) +
  scale_fill_manual(values = intervention_colors_highlight) 
ggsave("intervention_highlight.png", width = 10)
```

```{r plot-intervention}
# by age
ggplot(data_tidy_intervention, 
       aes(x = age, y = intervention_coded, color = intervention_coded)) +
  facet_wrap(vars(condition)) +
  geom_point() +
  scale_color_manual(values = intervention_colors) + 
  theme(legend.position = "none") 
```

### Difficulty of intervention
```{r intervention-diff}
# Plot: difficulty of intervention by condition
ggplot(data_tidy_intervention, 
       aes(x = condition, y = intervention_diff)) +
  # ggtitle("Difficulty of intervention by condition") +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.1) +
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5) +
  guides(fill = guide_legend(title = NULL)) +
  scale_y_continuous(name = "",
                     # name = "Would it be easy or hard to do that?",
                     labels = c("very easy", "a little easy", "a little hard", "very hard"))
ggsave("intervention_diff_condition.png", width = 7)


# Plot: difficulty of intervention by intervention type
ggplot(data_tidy_intervention, 
       aes(x = intervention_coded, y = intervention_diff)) +
  # ggtitle("Difficulty of intervention by target of intervention") +
  geom_point(position = position_jitter(width = 0.2, height = 0.075),
             size = 2, alpha = 0.3) +
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               geom = "linerange",
               size = 1) +
  stat_summary(fun = "mean",
               position = position_dodge(width = 0.8),
               geom = "point",
               shape = 21,
               color = "black",
               fill = "black",
               size = 5) +
  # scale_color_manual(values = condition_colors) +
  scale_x_discrete(name = "Target of intervention") +
  scale_y_continuous(name = "Would it be easy or hard to do that?",
                     labels = c("very easy", "a little easy", "a little hard", "very hard"))
ggsave("intervention_diff.png", width = 18)
```



## Models
### Possibility of change
```{r target-analysis-possibility-change}
# Possibility of change: linear model, controlling for difficulty of intervention
possibility_change_lm <- lm(possibility_change ~ condition + intervention_diff,
                            data = data)

# main effect of condition, controlling for intervention difficulty
possibility_change_lm %>% 
  aov() %>% 
  summary()

# compare all pairwise condition means (controlling for difficulty of intervention), FDR adjustment for all comparisons
possibility_change_lm %>% 
  emmeans("condition") %>% 
  pairs(adjust = "fdr") %>% 
  summary()

# compare conditions against chance
t.test(data %>% filter(condition == "biological") %>% select(possibility_change),
       mu = mean(1:4))

t.test(data %>% filter(condition == "cultural") %>% select(possibility_change),
       mu = mean(1:4))

t.test(data %>% filter(condition == "structural") %>% select(possibility_change),
       mu = mean(1:4))
```


```{r}
# Possibility of change: Bayesian linear model, controlling for difficulty of intervention
possibility_change_brm <- brm(possibility_change ~ condition + intervention_diff,
                              data = data,
                              file = "possibility_change_brm")
possibility_change_brm %>% 
  pp_check() # posterior predictive check looks weird because measure is actually ordinal, not continuous?

possibility_change_brm %>% 
  hypothesis("conditionstructural > 0") # Structural vs Internalist (biological)

possibility_change_brm %>% 
  hypothesis("conditionstructural - conditioninternalist_cultural > 0") # Structural vs Internalist (cultural)

possibility_change_brm %>% 
  hypothesis("conditioninternalist_cultural > 0") # Internalist (cultural) vs Internalist (biological)
```

### Normativity
```{r target-analysis-normativity}
# Normativity: linear model, controlling for difficulty of intervention
normativity_lm <- lm(normativity ~ condition + intervention_diff,
                     data = data)

# main effect of condition, controlling for intervention difficulty
normativity_lm %>% 
  aov() %>% 
  summary()

# compare all pairwise condition means (controlling for difficulty of intervention), FDR adjustment for all comparisons
normativity_lm %>% 
  emmeans("condition") %>% 
  pairs(adjust = "fdr") %>% 
  summary()

# compare conditions against chance
t.test(data %>% filter(condition == "biological") %>% select(normativity),
       mu = mean(1:6))

t.test(data %>% filter(condition == "cultural") %>% select(normativity),
       mu = mean(1:6))

t.test(data %>% filter(condition == "structural") %>% select(normativity),
       mu = mean(1:6))
```

```{r}
# Normativity: Bayesian linear model, controlling for difficulty of intervention
normativity_brm <- brm(normativity ~ condition + intervention_diff,
                       data = data,
                       file = "normativity_brm")

normativity_brm %>% 
  pp_check() # posterior predictive check looks weird because measure is actually ordinal, not continuous?

normativity_brm %>% 
  hypothesis("conditionstructural > 0") # Structural vs Internalist (biological)

normativity_brm %>% 
  hypothesis("conditionstructural - conditioninternalist_cultural > 0") # Structural vs Internalist (cultural)

normativity_brm %>% 
  hypothesis("conditioninternalist_cultural > 0") # Internalist (cultural) vs Internalist (biological)
```


### Switched context
```{r target-analysis-switched-context}
# Switched context: linear model, controlling for difficulty of intervention
switched_context_lm <- lm(switched_context ~ condition + intervention_diff,
                            data = data)

# main effect of condition, controlling for intervention difficulty
switched_context_lm %>% 
  aov() %>% 
  summary()
# 
# # compare all pairwise condition means (controlling for difficulty of intervention), FDR adjustment for all comparisons
# switched_context_lm %>% 
#   emmeans("condition") %>% 
#   pairs(adjust = "fdr") %>% 
#   summary()

# compare conditions against chance
t.test(data %>% filter(condition == "biological") %>% select(switched_context),
       mu = mean(1:4))

t.test(data %>% filter(condition == "cultural") %>% select(switched_context),
       mu = mean(1:4))

t.test(data %>% filter(condition == "structural") %>% select(switched_context),
       mu = mean(1:4))
```


```{r}
# Switched context: Bayesian linear model, controlling for difficulty of intervention
switched_context_brm <- brm(switched_context ~ condition + intervention_diff,
                              data = data,
                              file = "switched_context_brm")
switched_context_brm %>% 
  pp_check() # posterior predictive check looks weird because measure is actually ordinal, not continuous?

switched_context_brm %>% 
  hypothesis("conditionstructural > 0") # Structural vs Internalist (biological)

switched_context_brm %>% 
  hypothesis("conditionstructural - conditioninternalist_cultural > 0") # Structural vs Internalist (cultural)

switched_context_brm %>% 
  hypothesis("conditioninternalist_cultural > 0") # Internalist (cultural) vs Internalist (biological)
```


### Target of intervention
Analyze whether counts of coded responses are independent of condition, using Fisher's exact test (rather than chi-square because of small sample size).
```{r}
# Fisher's exact test: are the proportion of responses different across the 3 conditions?
fisher.test(data_intervention_counts %>% select(-condition), 
            workspace = 2e8)
```

#### Modify Zarpies biology
```{r intervention-modify-Zarpies-biology-glm}
# Target of intervention: modify Zarpies biology: logistic regression, controlling for difficulty of intervention 
glm(modify_group_biology ~ condition + intervention_diff,
    family = "binomial",
    data = data_intervention) %>% 
  summary()
```
If observe quasi-complete separation in the logistic regression for the internalist_cultural condition, implement logistic regression with Firth bias-reduction. Otherwise proceed with glm.

```{r intervention-modify-Zarpies-biology-brglm, warning=FALSE}
modify_group_biology_glm <- glm(modify_group_biology ~ condition + intervention_diff,
    family = "binomial",
    data = data_intervention)

# ANOVA for main effect of condition, controlling for intervention difficulty? --> yes
modify_group_biology_glm %>%
  aov() %>%
  summary()

# simultaneous pairwise comparisons (condition 1v2, 2v3, 1v3), adjusted --> biological > cultural/structural
modify_group_biology_glm %>% 
  emmeans("condition") %>% 
  pairs(adjust = "FDR") %>% 
  summary()

# # more than half in biological condition? 
# binom.test(x = data_intervention %>% filter(condition == "biological") %>% pull(modify_group_biology) %>% sum(),
#            n = data_intervention %>% filter(condition == "biological") %>% pull(modify_group_biology) %>% length(),
#            p = 0.5, # compare against half
#            alternative = "two.sided")
```

```{r}
# Target of intervention: modify Zarpies biology: Bayesian logistic regression, controlling for difficulty of intervention
modify_Zarpies_biology_brm <- brm(modify_Zarpies_biology ~ condition + intervention_diff,
    family = "binomial",
    data = data.intervention,
    file = "modify_Zarpies_biology_brm")

modify_Zarpies_biology_brm %>% 
  pp_check() 

modify_Zarpies_biology_brm %>% 
  hypothesis("conditionstructural < 0") # Structural vs Internalist (biological)

modify_Zarpies_biology_brm %>% 
  hypothesis("conditionstructural - conditioninternalist_cultural < 0") # Structural vs Internalist (cultural)

modify_Zarpies_biology_brm %>% 
  hypothesis("conditioninternalist_cultural < 0") # Internalist (cultural) vs Internalist (biological)
```

#### Modify Zarpies beliefs/culture
```{r}
# Target of intervention: modify Zarpies beliefs/culture: logistic regression, controlling for difficulty of intervention 
glm(modify_group_beliefs_culture ~ condition + intervention_diff,
    family = "binomial",
    data = data_intervention) %>% 
  summary()
```
If observe quasi-complete separation in the logistic regression for the internalist_cultural condition, implemented logistic regression with Firth bias-reduction. Otherwise proceed with glm. 

```{r intervention-modify-Zarpies-beliefs-culture-brglm, warning=FALSE}
modify_group_beliefs_culture <- brglm(modify_group_beliefs_culture ~ condition + intervention_diff,
    family = "binomial",
    data = data_intervention)

# main effect of condition, controlling for intervention difficulty? (ANOVA)
modify_group_beliefs_culture %>%
  aov() %>%
  summary()

# simultaneous pairwise comparisons (condition 1v2, 2v3, 1v3), adjusted
modify_group_beliefs_culture %>% 
  emmeans("condition") %>% 
  pairs(adjust = "FDR") %>% 
  summary()

# # more than half in cultural condition? 
# binom.test(x = data_intervention %>% filter(condition == "cultural") %>% pull(modify_group_beliefs_culture) %>% sum(),
#            n = data_intervention %>% filter(condition == "cultural") %>% pull(modify_group_beliefs_culture) %>% length(),
#            p = 0.5, # compare against half
#            alternative = "two.sided")
```

```{r}
# Target of intervention: modify Zarpies beliefs/culture: Bayesian logistic regression, controlling for difficulty of intervention
modify_Zarpies_beliefs_culture_brm <- brm(modify_Zarpies_beliefs_culture ~ condition + intervention_diff,
    family = "binomial",
    data = data.intervention,
    file = "modify_Zarpies_beliefs_culture_brm")

modify_Zarpies_beliefs_culture_brm %>% 
  pp_check() 

modify_Zarpies_beliefs_culture_brm %>% 
  hypothesis("conditionstructural > 0") # Structural vs Internalist (biological)

modify_Zarpies_beliefs_culture_brm %>% 
  hypothesis("conditionstructural - conditioninternalist_cultural < 0") # Structural vs Internalist (cultural)

modify_Zarpies_beliefs_culture_brm %>% 
  hypothesis("conditioninternalist_cultural > 0") # Internalist (cultural) vs Internalist (biological)
```

#### Change environment
```{r intervention-change-environment-brglm, warning=FALSE}
# Target of intervention: logistic regression, controlling for difficulty of intervention
modify_environment_glm <- glm(modify_environment ~ condition + intervention_diff,
    family = "binomial",
    data = data_intervention) 
```

If observe quasi-complete separation in the logistic regression for the internalist_cultural condition, implemented logistic regression with Firth bias-reduction. Otherwise proceed with glm.

```{r}
# main effect of condition, controlling for intervention difficulty? (ANOVA)
modify_environment_glm %>%
  aov() %>%
  summary()

# simultaneous pairwise comparisons (condition 1v2, 2v3, 1v3), adjusted
modify_environment_glm %>% 
  emmeans("condition") %>% 
  pairs(adjust = "fdr") %>% 
  summary()

# odds ratios?
exp(cbind(coef(modify_environment_glm), confint(modify_environment_glm)))  


# # more than half in structural condition? 
# binom.test(x = data_intervention %>% filter(condition == "structural") %>% pull(modify_environment) %>% sum(),
#            n = data_intervention %>% filter(condition == "structural") %>% pull(modify_environment) %>% length(),
#            p = 0.5, # compare against half
#            alternative = "two.sided")
```

```{r}
# Target of intervention: acquire okinberries: Bayesian logistic regression, controlling for difficulty of intervention
acquire_okinberries_brm <- brm(modify_Zarpies_beliefs_culture ~ condition + intervention_diff,
    family = "binomial",
    data = data.intervention,
    file = "acquire_okinberries_brm")

acquire_okinberries_brm %>% 
  pp_check() 

acquire_okinberries_brm %>% 
  hypothesis("conditionstructural > 0") # Structural vs Internalist (biological)

acquire_okinberries_brm %>% 
  hypothesis("conditionstructural - conditioninternalist_cultural > 0") # Structural vs Internalist (cultural)

acquire_okinberries_brm %>% 
  hypothesis("conditioninternalist_cultural > 0") # Internalist (cultural) vs Internalist (biological)
```

# Exploratory analysis
## Correlations between measures
```{r }
ggplot(data, 
       aes(x = switched_context, y = normativity)) +
  facet_wrap(vars(condition)) +
  geom_point(position = position_jitter(width = 0.1, height = 0.1),
             size = 2, alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE, level = 0.95) +
  scale_y_continuous(name = "non-conformity of group member",
                     # name = "attitude towards non-conformity",
                     breaks = c(1, 2, 3, 4, 5, 6),
                     labels = c("very, very good", "pretty good", "a little good", "a little bad", "pretty bad", "very, very bad")) +
  scale_x_continuous(name = "generalization to switched context",
                     # name = "Prediction about member outside context",
                     breaks = c(1, 2, 3, 4),
                     labels = c("[same berry]", "", "", "[other berry]")) 
ggsave("switched_context_normativity.png", width = 12)

```

## Age
```{r possibility-change-age}
lm(possibility_change ~ condition * age + intervention_diff,
   data = data) %>% 
  anova()
```
```{r normativity-age}
lm(normativity ~ condition * age + intervention_diff,
   data = data) %>% 
  anova()
```

```{r switched-context-age}
lm(switched_context ~ condition * age + intervention_diff,
   data = data) %>% 
  anova()
```


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
